\tool: Revisiting BadUSB with Type-C

### 2021-03-12 response_letter/response-letter.tex

\documentclass[oneside, 11pt]{article}
\usepackage{times,fullpage,indentfirst,graphicx,setspace,subfigure,epsfig,wasysym,url,hyperref}
\usepackage{booktabs}
\usepackage{appendix}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{array}
%\usepackage{ulem}

\topmargin -0.17in

\hoffset -0.1in

\textwidth 6.6in

\oddsidemargin 0.1in

\textheight 9.2in

\newenvironment{cvl}{\begin{list}{$\bullet$}{
\setlength{\leftmargin}{0.3in} \setlength{\labelsep}{0.07in}
\setlength{\labelwidth}{0.17in} \setlength{\rightmargin}{0.0in}
\setlength{\topsep}{0.000in} \setlength{\partopsep}{0.000in}
\setlength{\parskip}{0.000in} \setlength{\parsep}{0.005in}
\setlength{\itemsep}{0.005in}}}{\end{list}}

\begin{document}

\setcounter{page}{1}
%\pagestyle{empty}

\newcommand{\TheName}{\textsc{Fine-CFI}}

\title{Response to Reviewers on ``\TheName{}: Fine-grained Control-Flow
Integrity for Operating System Kernels''}

\author{Jinku Li, Xiaomeng Tong, Fengwei Zhang, and Jianfeng Ma \\
\\
\vspace{0.2in}
\begin{small}
\begin{tabular}{cc}
jkli@xidian.edu.cn, txmxidian@gmail.com, fengwei@wayne.edu, jfma@mail.xidian.edu.cn\\
\end{tabular}
\end{small}
}

\date{}
\maketitle

%%\doublespacing
%\renewcommand{\baselinestretch}{1.8}
%%\baselineskip{8mm}
%\bibliographystyle{plain}
%
%\end{spacing}
%%\vspace{-5mm}

We would like to deeply thank the anonymous reviewers and the Associate
Editor for their timely, constructive comments. Your reviews provide
valuable and unique insight that we have taken into great consideration
to make this revision possible. In this document, please find our summarized
revisions as well as detailed response to the reviewers' comments.

\section{Revision Summary}
Based on the reviews' comments, we have made major revisions in the
following three aspects. And we have also uploaded a PDF \textbf{diff} file to the
ScholarOne system for the reviewers.

\begin{itemize}

\item %\smallskip
\noindent
First, we have modified the prototype of \TheName{} to prevent attacks by
corrupting only the CS in the interrupt context.

In the new prototype,
we provide protection for the CS as well as the IP in the context information
when an interrupt occurs. To this end, we need to instrument the \emph{iret}
instruction to verify the CS/IP pair for the interrupt return. Specifically,
we insert seven instructions before \emph{iret} instruction
in function \emph{irq\_return()}. We use two \emph{mov} instructions
(i.e., \emph{mov 0x10(\%rsp),\%r12} and \emph{mov 0x18(\%rsp),\%r13}) to dump
the CS/IP pair in current VM kernel stack (in \emph{0x10(\%rsp)} and \emph{0x18(\%rsp)})
into \emph{\%r12} and \emph{\%r13} registers, which are pre-pushed into the
stack (with \emph{push \%r12} and \emph{push \%r13}) for later restoring
(with \emph{pop \%r13} and \emph{pop \%r12}). After that, a \emph{vmcall}
instruction is executed to exit from the VM and enter the hypervisor, so that
we can verify the dumped data in \emph{\%r12} and \emph{\%r13} registers.
A new instrumentation example for interrupts is shown in
Figure 5 (see Section III.C, pp.9).

We have re-evaluated the performance for the new prototype, and the
results show that the overhead is less than $10$\% on average.
The details can be found in Section IV.B, pp.11-13.

\item %\smallskip
Second, the evaluation has been greatly expanded in the revision.

In the security evaluation of our system, we have figured out the
remaining gadgets in the original and instrumented Linux kernel
using the open-source tool ROPgadget. As a result, ROPgadget found
44,063 gadgets in the original Linux kernel and 841 gadgets in the
instrumented Linux kernel. We checked all these 841 gadgets and
confirmed that none of them can be reached through a control flow
which is allowed by our fine-grained CFG. Therefore, none of these
gadgets could be leveraged to launch an effective ROP attack.
The details can be found in Section IV.A, pp.11.

In the performance evaluation of our system, we have introduced 3 new
tests to our system. (1) In order to further measure the
impact on real-world applications introduced by \TheName{}, we have
selected five representative real-world applications in Phoronix Test
Suite, i.e., compress-7zip, postmark, nginx, cachebench, and network-loopback,
which stand for the performance behaviors in processor, disk, system, memory,
and network, respectively, to evaluate the performance overhead of our system.
%(2) To further show an intuitive comparison with the user-level CFI implementations,
(2) To further demonstrate the performance overhead introduced by \TheName{},
we have implemented our approach to four benchmarks in SPEC CPU2006 benchmarking
suite, i.e., 401.bzip2, 403.gcc, 429.mcf, and 458.sjeng for evaluation.
(3) For the above C benchmark programs (i.e., 401.bzip2, 403.gcc, 429.mcf, and 458.sjeng),
we have also achieved the goal to break the results down by only instrumenting
indirect call/jmp (\emph{New-icall}) or call/ret (\emph{New-ret}) instructions, to
see the impact on the forward/backward edge protection.
The results show that the performance overhead is less than $10$\% on average.
The details can be found in Section IV.B, pp.11-13.

\item %\smallskip
Third, we have revised Section II.B carefully to address a few concerns raised by the reviewers.

(1) We have provided a formal definition of \emph{struct location vector}.
In particular, we define the \emph{struct location vector} of a function pointer
as the location of the function pointer member in a (nested) struct.
To better represent the cases in nested structs, we use the name of the
struct, the element's order number, and the nested member's order numbers
to reach the function pointer member in the struct to denote its
\emph{struct location vector} (see Section II.B, pp.4).

(2) We have introduced a more high-level description of our pointer
analysis with a basic worklist algorithm that does not require compiler
background knowledge to understand (see Algorithm 1, pp.4).
After that, to describe our algorithm more intuitively, we leverage a simple
example program to present the process to determine the point-to sets of
indirect function calls (see Figure 1 and 2, pp.5).

(3) We have made our main innovation clearer in the revision.
Specifically, the main innovation of our retrofitted point-to analysis is that
we introduce a new vector, called \emph{struct location vector}, to infer the
targets for indirect function calls. This is reasonable as we observe that
there are a large number of function pointer initializations and assignments inside
struct variables in kernel space, and the function pointer locates in the
same field of the struct in its lifetime, i.e., from the initialization or assignment to
be consumed by indirect function calls. Combining \emph{struct location vector}
with function signature-based policy, it largely reduces the number of targets
of indirect call/jmp instructions -- average 13.14 for each indirect call/jmp
instruction (see Section II.B, pp.4).

\end{itemize}

\smallskip
Next, we present our detailed response to individual reviewer's comments.

\section{Response to Reviewer One}

\noindent {\bf This paper proposes a novel CFI (Control Flow Integrity)
approach for operating system kernels, named \TheName{}. \TheName{} uses a
static analysis approach to determine a fine-grained CFG (Control Flow
Graph) of the kernel, then enforces control flow to stay within that CFG.
Moreover, it offers a hypervisor-based protection against corruption
of interrupt context data.

The work is certainly of good quality. Most importantly, it combines fine
granularity with low overhead, which is a significant improvement over
previous work.}

{\em Authors response:}
Thanks for the summary and favorable comments.

\smallskip
\smallskip
\smallskip
\noindent {\bf However, there is a major issue that needs to be addressed.
Through the paper, the authors state that the hypervisor-based protection
covers the CS/IP pair in the interrupt context. However, the final prototype
only covers IP (and this is indicated in just a footnote).
Moreover, not protecting CS can have a serious security impact: it can
allow an attacker to return from an interrupt to user code (IP, not
corrupted) with kernel privileges (by corrupting the CPL in CS).
This clearly only applies when SMEP is not present, but \TheName{} makes
no assumptions on SMEP. Since leaving CS unprotected has an actual impact,
I believe the prototype should be modified to include it and the performance
re-evaluated. Evaluation of the main CFI mechanism is not affected.}

{\em Authors response:}
Thank you very much for the great comments! We have followed your suggestion
and modified the prototype to prevent attacks by corrupting only the
CS. In the new prototype, we provide protection for the CS as well as the IP.
To achieve that, we need to instrument the \emph{iret} instruction to
verify the CS/IP pair for the interrupt return. Specifically,
we insert seven instructions before \emph{iret} instruction
in function \emph{irq\_return()}. We use two \emph{mov} instructions
(i.e., \emph{mov 0x10(\%rsp),\%r12} and \emph{mov 0x18(\%rsp),\%r13}) to dump
the CS/IP pair in current VM kernel stack (in \emph{0x10(\%rsp)} and \emph{0x18(\%rsp)})
into \emph{\%r12} and \emph{\%r13} registers, which are pre-pushed into the
stack (with \emph{push \%r12} and \emph{push \%r13}) for later restoring
(with \emph{pop \%r13} and \emph{pop \%r12}). After that, a \emph{vmcall}
instruction is executed to exit from the VM and enter the hypervisor, so that
we can verify the dumped data in \emph{\%r12} and \emph{\%r13} registers.
A new instrumentation example for interrupts is shown in
Figure 5 (see Section III.C, pp.9).

We have re-evaluated the performance for the new prototype, and the
results show that the overhead is less than $10$\% on average.
As well, we have introduced several other benchmarks to make further
evaluation for our system. The details can be found in Section IV.B, pp.11-13.

%Thank you very much for the constructive comments. After your explanation,we
%realize that it is a big mistake to leave CS unprotected. As a result, we rebuild
%the entire system to make sure CS is protected including the instrumentation for
%dumping CS before iret in guest kernel and the backup/verification of CS in KVM.
%We have revised it in the revision (see Section III.C,pp.9). Then, we re-evaluate
%the performance for the whole system and the result shows that the overhead
%is acceptable. At the same time, we have introduced other benchmark tests to
%make the evaluation of performance more accurately (see Section IV.B,pp.10-11).

\smallskip
\smallskip
\smallskip
\noindent {\bf There are also other improvements I would like to see:}

\noindent {\bf 1) Expand and clarify on ret2usr attacks. The classic ret2usr involves
corrupting non-interrupt control data (e.g., a kernel function pointer),
and kernel CFI mitigates it. The kind of ret2usr that requires hypervisor
protection involves corrupting the interrupt context and is not covered
by the provided reference ([25]). I would also appreciate if you touched
upon SMEP and SMAP, as they are effective hardware countermeasures to
classic ret2usr. }

{\em Authors response:}
Thanks for your suggestion. We have made expansion and clarification on the
two kinds of ret2usr attack in the revision (see Section I, pp.2).
As pointed out by you, the classic ret2usr attacks only corrupt
non-interrupt (usual) control data in kernel space, e.g., a kernel function pointer
or return address. However, the novel ret2usr attacks could corrupt IP and CS
in the interrupt context to transfer execution control-flow to the user-space code
controlled by attackers with kernel privileges. As a result, we also need to
provide protection for the control data in the
interrupt context, as well as the usual control data in kernel space.

At the same time, in the revision, we have presented several feasible
attacks to bypass SMEP/SMAP, and explained why all of them can be defeated by
\TheName{} (see Section IV.A, pp.11).
Specifically, it has been showed that SMEP/SMAP could be bypassed with kernel code-reuse
attacks, although they are effective hardware countermeasures to classic ret2usr attacks.
Popov provides a method to bypass SMEP by tampering the function pointer with
kernel function \emph{native\_write\_cr4()} and passing a controlled argument with
the bit 20 of CR4 register cleared to disable it [1].
Nikolenko shows another trick to disable SMEP by combining several useful kernel gadgets
and pivoting the stack for clearing the bit, or bypass SMAP by abusing vDSO [2].
However, \TheName{} prevents both the kernel code-reuse attacks and the ret2usr attacks,
by providing fine-grained CFI protection and the control data protection in the interrupt context.
Thus, \TheName{} is immune to the above attacks.

% FIXME: a comment, why do we add "here" at the end of the references? is there any purticular reason?
[1] ``Cve-2017-2636: exploit the race condition in the n\_hdlc linux kernel driver bypassing smep.''\\
https://a13xp0p0v.github.io/2017/03/24/CVE-2017-2636.html.

[2] ``Practical smep/smap bypass techniques on linux.''\\
http://www.syscan360.org/slides/2016\_SG\_Vitaly\_Nikolenko\_Practical\_SMEP\_Bypass\_Techniques.pdf.
%(\%20 and \_)

%However, our fine-grained CFI enforcement and hypervisor-based protection not only
%effectively prevent ret2usr attacks, but also effectively prevent kernel code-reuse attacks,
%as we have eliminated all the usable gadgets by limiting the control flow in the fine-grained CFG
%and verified all the interrupt control data.

%Thanks for your suggestion. We have expanded and described the two kinds of
%ret2usr attacks in  the revision (see Section I,pp.2). At the same time,
%we discussed the two existing feasible attacks for bypassing SMEP and
%explained why both of them can be defeated by our \TheName{} (see Section IV.A,pp.10).

\smallskip
\smallskip
\smallskip
\noindent {\bf 2) Clarify the instrumentation of direct calls. In Section
III.B the authors mention the replacement of 50,677 direct calls. Why are
they replaced, when the integrity of kernel code is assumed in Section II.A? }

{\em Authors response:}
Indeed, the reason why it instruments direct call instructions is due to
the adoption of \emph{indexed hooks} approach to enforce CFI protection.

Specifically, based on the observation that existing control data (e.g.,
function pointers or return addresses) have a set of legitimate jump targets,
\emph{indexed hooks} precalculates them into (protected) jump tables and then replaces
these control data with their indexes to these tables.
Note that the jump tables are read-only and thus can be protected with
the hardware-based page-level protection.
For each ret instruction, its jump table (i.e., return table) contains all the return
addresses it may return to according to the CFG. With that, \emph{indexed hooks} leverages
the extended compiler \emph{LLVM} to instrument all the return address-related instructions by replacing the
return address with a return table index. In the high level, to provide protection for
return addresses, a ``call dst'' instruction is instrumented into ``push \$ret\_table\_index; jmp dst'',
and a ``ret'' instruction is instrumented into ``pop \%reg; jmp *RetTable(\%reg)''.
We have made clarification in the revision (see Section III.B, pp.8).

%Thanks a lot. A ret instruction will transfer the control flow to the instruction that
%immediately follows a just executed call instruction, whatever it is a
%direct call or a indirect call. As a result, as we instrument all ret
%instructions, any call instruction must be replaced to push the index
%rather than the real return address on stack. In other words, the direct
%call instruction also needs to be instrumented. The description can be
%found in Section III.B,pp.8.

\smallskip
\smallskip
\smallskip
\noindent {\bf 3) Explicitly mention the performance numbers for other
kernel CFI implementations when comparing them to \TheName{}, as not all
readers are familiar with them. }

{\em Authors response:}
Thanks for your suggestion. In the revision, we have explicitly compared the
performance overhead of KCoFI and [1] to \TheName{}. The results indicate
that the performance overhead of \TheName{} is smaller than the other two
systems (see Section IV.B, pp.11-12).

Specifically, in the Phoronix Test Suite, for postmark benchmark which is used
to measure the file system performance, \TheName{} only incurs $7.69$\%
overhead while KCoFI incurs $1.96$x on average. At the same time, in the evaluation
results of LMbench, \TheName{}'s maximum overhead for fork+exit operation is
only $11.05$\% while KCoFI incurs $3.50$x overhead on average.
On the other hand, in the evaluation results of UnixBench, \TheName{}
incurs $7.20$\% overhead for a Linux kernel, while [1] incurs $11.91$\% overhead
for a FreeBSD kernel.

[1] X. Ge, N. Talele, M. Payer, and T. Jaeger, ``Fine-grained control-flow
integrity for kernel software,'' in Security and Privacy (EuroS\&P), 2016 IEEE
European Symposium on, pp.179-194, IEEE, 2016.

%Thanks for your suggestion. We have explicitly figured out the performance
%overheads for other kernel CFI implementations when comparing them to our
%\TheName{} (see Section IV.B,pp.11).

\smallskip
\smallskip
\smallskip
\noindent {\bf 4) Define the struct location vector more formally.
Right now it is defined through examples, and while it can be understood
it would be better to have an explicit definition of it, especially
because there can be multiple indexes for nested fields, which is not
immediately clear from Section II.B.}

{\em Authors response:}
Thanks for your suggestion. In the revision, we have provided the formal
definition of \emph{struct location vector} (see Section II.B, pp.4).
In particular, we define the \emph{struct location vector} of a function pointer
as the location of the function pointer member in a (nested) struct.

To better represent the cases in nested structs, we use the name of the
struct, the element's order number, and the nested member's order numbers
to reach the function pointer member in the struct to denote its
\emph{struct location vector}. Thus, the \emph{struct location vector} of a
function pointer is denoted as
\emph{(\%struct.name, ele\_order, mem\_order\_$1$, ... , mem\_order\_$i$, ...)}
(\emph{ele\_order} denotes the element' order number in a \emph{\%strut.name}\_typed
array, and \emph{mem\_order\_$i$} denotes the member's order number of layer
\emph{$i$} in \emph{\%struct.name} struct to reach the function pointer; $i$$>=1$).
For example, vector \emph{(\%struct.sb,$0$,$2$)} denotes that a function pointer
locates at the \emph{$2$nd} member of layer $1$ in a \emph{\%struc.sb} struct, which
is the \emph{$0$th} element in a \emph{\%struct.sb}-typed array.

%\begin{itemize}
%\item (\%struct.name, X, i, j, k, ...), respectively denotes the name of struct type,
%the Xth element in a struct array, the ith member inside a \%struct.name-typed
%variable, the jth member inside a \%struct.name\_i-typed variable, the kth
%member inside a \%struct.name\_j-typed variable and so on.
%\end{itemize}

\smallskip
\smallskip
\smallskip
\noindent {\bf 5) In Figure 1(b), there seems to be an omission that
is not indicated: the initialization (presumably from a stack allocation)
of \%1 and \%2 is not present. While not relevant for the analysis,
the omission should be indicated. }

### 2021-03-12 WOOT/Files/introduction.tex

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
victim's graphical interface during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.  
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.  
Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers are involved in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

@@

The rest of this paper is structured as follows.  Section~\ref{sec:background}
provides the background of \ac{USB} specification.  Section~\ref{sec:related_work}
introduces the existing work of \ac{USB} security from the aspects of attacking and
defense, respectively.  In Section~\ref{sec:badusb}, we present the threat model
and the overall implementation of \tool in three different modes.  The
experiments and user study we conducted are featured in
Section~\ref{sec:experiment}.  We present the possible countermeasures of \tool
in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach
are discussed in Section~\ref{sec:discussion}, and the conclusion lies in
Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}

>>>>

In this work, we addressed the limitations mentioned
above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
victim's \ac{GUI} during attacks.  Combining it with the emulation
of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
performing precise attacks.  
%We did experiments to verify that \tool could also
%bypass some countermeasures for BadUSB since they often rely on interaction
%with the graphical interface.  
Moreover, we implemented multiple attacking
modes of \ac{USB} attacks based on our approach to verify its effectiveness,
including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
efficiency and performance of \tool, we designed a filtering algorithm to
preprocess the video data before network transmission.  Moreover, we conducted
a series of experiments for each attack mode as well as for different types of
devices, including smartphones, personal computers, and tablet computers, to
validate the usability of \tool.  We also conducted a user study for attacks in
sharing power banks, one of the application scenarios of \tool.  During the
user study, we obtained a large amount of sensitive data through \tool, since
users are usually unconscious of the necessity to check the \ac{USB} devices they
plugged in for security purposes.  
Ten volunteers participated in the user study.
Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
After the validation of our attack model, we
proposed several defense methods as countermeasures, including external
hardware authorization, distrust-by-default, etc.  It is worth noting that we
designed a method, called isolated \ac{UI} rendering, to separate the user interface
into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
%\shuqing{Case study, evaluation, notable results.}

@@

The rest of this paper is structured as follows.  Section~\ref{sec:background}
provides the background of \ac{USB} specification.  Section~\ref{sec:related_work}
introduces the existing works of \ac{USB} security from the aspects of attacking and
defense, respectively.  In Section~\ref{sec:badusb}, we present the threat model
and the overall implementation of \tool in three different modes.  The
experiments and user study we conducted are featured in
Section~\ref{sec:experiment}.  We present the possible countermeasures of \tool
in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach
are discussed in Section~\ref{sec:discussion}, and the conclusion lies in
Section~\ref{sec:conclusion}.
%\shuqing{Fill in after the structure is finalized.}

### 2021-03-12 WOOT/Files/related_work.tex

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Although \ac{USB} 2.0 does not
support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
from the victim without permission. However, in JFC, this data exfiltration is not
combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
capability.

@@

% Using USB for information leakage
As a data transmission protocol, \ac{USB} inevitably leaks electromagnetic signals
to the environment which may contain sensitive information. Leveraging this
physical phenomenon, previous works~\cite{smartphone,
poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
eavesdrop on leaked signals and recover the sensitive data. In a similar fashion, USBee\cite{usbee} and TURNIPSCHOOL\cite{turnip} emit electromagnetic emissions by data injection on the bus
with the connected \ac{USB} devices as an RF transmitter and USBKiller\cite{usbkiller}
inject analog
power to cause physical damage to the host machine. Even though the data,
including the video data, could be recovered in this way, these attacks for
executing malicious code are too difficult to work, and invisibility is a
problem that cannot be ignored due to the spatial locality of radio frequency.

Since \ac{USB} 3.1 was introduced with \ac{USB} Type-C in 2013, display port and HDMI
connectors have been provided by \ac{USB} Type-C, transferring of video data can be
combined with the other attacks, like protocol masquerading,  protocol
corruption, and code injection. This has paved the path for our \tool.

It is worth noting that our \tool is different from JFC~\cite{JFC}. Juice Filming Attacks cannot control the attacked device, it can only video-capture user inputs during charging. However, our \tool can control the attacked device at the same time as monitoring the screen, which enhances the efficiency of stealing users' private data.

@@

From the hardware perspective, the BadUSB attack requires \mbox{`D-' and `D+'} pins which
are defined by the protocol to transmit data. Without these pins, data cannot 
be transferred via a \ac{USB} cable. Based
on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the \mbox{`D-' and `D+'} connection while leaving power pins intact. However, this method poses
a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
stops all \ac{USB} functions other than charging.

Under the premise of ensuring the full functionality of \ac{USB} devices, some works
improve the security while establishing connection. Windows Defender
ATP~\cite{windenfenderwhite} maintains a whitelist of \ac{USB} devices, only devices
on the whitelist are allowed to communicate with the host. This prevents all
potential attacks from untrusted devices, however, this requires users to have a
certain security awareness and technical background to maintain a valid
whitelist. For example, a naive user may add the \ac{USB} device from unknown
sources to his/her whitelist without precaution. Fortunately, some designs have proposed to overcome
this drawback. For instance, Mohammadmoradi \emph{et al.}~\cite{mohammadmoradi2018making}\shuqing{check name} propose a strategy to generate such a
whitelist automatically. This strategy first generates a unique fingerprint for
each device based on its functionality. Then these fingerprints are used to
maintain a secure and valid whitelist of \ac{USB} devices. There is another work
mediating \ac{USB} connectivity for industrial control. TMSUI~\cite{yang2015tmsui}
relies on the rich experience of administrators to build a whitelist. However, some
modified \ac{USB} devices may hide their real functionality from the user.

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decide whether to authorize. When a device
is plugged in, GoodUSB limits its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected if they make a different claim 
that does not match the authorization results. 
USBeSafe\cite{usbesafe} analyses the 
feature vector constructed with the data collected from \acp{URB}, 
detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
a alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.
Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience. It can detect the presence of the user, block malicious device in the user's absence until the session is unlocked.

@@

In addition to injection attacks, data theft attack is also one of the focuses
of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
exists an attack called JFC~\cite{JFC} which abuses the \ac{MHL}
standard to steal video stream from the victim. In order to mitigate this
issue, Meng et al.~\cite{meng2018252} proposed a statistical model using status
like GPU/CPU usage to detect JFC attacks.

>>>>

% USB protocol attacks
In the field of \ac{USB} security, protocol masquerading is also a widely used
attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
devices can hide their real functionality with re-written
firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
These works rewrite the firmware of a normal-looking flash drive, which allows
it to act like other devices. When these modified drives are connected to the
host, they could be recognized as a keyboard or mouse. Then the attacker can
execute malicious payloads as they were using the victim's devices. Due to the
limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
attacks~\cite{badusb} are unable to obtain video feedback from the victim
as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Although \ac{USB} 2.0 does not
support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
from the victim without permission. However, in JFA, this data exfiltration is not
combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
capability.

@@

% Using USB for information leakage
As a data transmission protocol, \ac{USB} inevitably leaks electromagnetic signals
to the environment which may contain sensitive information. Leveraging this
physical phenomenon, previous works~\cite{smartphone,
poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
eavesdrop on the leaked signals and recover the sensitive data. In a similar fashion, USBee\cite{usbee} and TURNIPSCHOOL\cite{turnip} emit electromagnetic emissions by data injection on the bus
with the connected \ac{USB} devices as an RF transmitter and USBKiller\cite{usbkiller}
inject analog
power to cause physical damage to the host machine. Even though the data,
including the video data, could be recovered in this way, these attacks for
executing malicious code are too difficult to work, and invisibility is a
problem that cannot be ignored due to the spatial locality of radio frequency.

Since \ac{USB} 3.1~\cite{usb31} was introduced with \ac{USB} Type-C in 2013, DisplayPort and HDMI
connectors have been provided by \ac{USB} Type-C, transferring of video data can be
combined with the other attacks, like protocol masquerading,  protocol
corruption, and code injection. This has paved the path for our \tool.

It is worth noting that our \tool is different from JFA~\cite{JFC}. Juice Filming Attacks cannot control the attacked device, it can only video-capture user inputs during charging. However, our \tool can control the attacked device at the same time as monitoring the screen, which enhances the efficiency of stealing users' private data.

@@

From the hardware perspective, the BadUSB attack requires \mbox{`D-' and `D+'} pins which
are defined by the protocol to transmit data. Without these pins, data cannot 
be transferred via a \ac{USB} cable. Based
on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
channels by adding a blocker in the connector. This blocker can cut off the \mbox{`D-' and `D+'} connection while leaving the power pins intact. However, this method poses
a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
stops all \ac{USB} functions other than charging.

Under the premise of ensuring the full functionality of \ac{USB} devices, some works
improve the security while establishing connection. Windows Defender
ATP~\cite{windenfenderwhite} maintains a whitelist of \ac{USB} devices, only devices
on the whitelist are allowed to communicate with the host. This prevents all
potential attacks from untrusted devices, however, this requires users to have a
certain security awareness and technical background to maintain a valid
whitelist. For example, a naive user may add the \ac{USB} device from unknown
sources to his/her whitelist without precaution. Fortunately, some designs have been proposed to overcome
this drawback. For instance, Mohammadmoradi \emph{et al.}~\cite{mohammadmoradi2018making}\shuqing{check name} propose a strategy to generate such a
whitelist automatically. This strategy first generates a unique fingerprint for
each device based on its functionality. Then these fingerprints are used to
maintain a secure and valid whitelist of \ac{USB} devices. There is another work
mediating \ac{USB} connectivity for industrial control. TMSUI~\cite{yang2015tmsui}
relies on the rich experience of administrators to build a whitelist. However, some
modified \ac{USB} devices may hide their real functionality from the user.

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decide whether to authorize. When a device
is plugged in, GoodUSB blocks its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected if they make a different claim 
that does not match the authorization results. 
USBeSafe\cite{usbesafe} analyses the 
feature vector constructed with the data collected from \acp{URB}, 
detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
an alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.
Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience. It can detect the presence of the user, block malicious devices in the user's absence until the session is unlocked.

@@

In addition to injection attacks, data theft attack is also one of the focuses
of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
exists an attack called JFA~\cite{JFC} which abuses the \ac{MHL}
standard to steal video stream from the victim. In order to mitigate this
issue, Meng et al.~\cite{meng2018252} propose a statistical model using status
like GPU/CPU usage to detect JFA attacks.
